Evaluating Modern vs. Older Buildings: Detailed Analysis on the Apartment Building Evaluation 2023

### 2024-01-22 Output/Paper/BuildingScoreAnalyze-2023.qmd
renamed files

---
title: "Evaluating Modern vs. Older Buildings: Detailed Analysis on the Apartment Building Evaluation 2023"
author: "Zhijun Zhong"
thanks: "Files, Codes and Paper are Availiable at https://github.com/JerrZzzz/Paper-1.git"
date: "today"
date-format: "long"
abstract: "This paper utilizes the Apartment Building Evaluation data from OpenDataToronto to investigate the common renter criteria that a building's construction year is a crucial factor in selecting a residence. Additionally, we compares scores across various aspects, such as windows and building cleanliness, for buildings constructed in specific years, further testing renters' theories."
format: pdf
editor: visual
toc: true
number-sections: true
bibliography: ref.bib
---

>>>>

---
title: "Evaluating Modern vs. Older Buildings: Detailed Analysis on the Apartment Building Evaluation 2023"
author: "Zhijun Zhong"
thanks: "Files, Codes and Paper are Availiable at https://github.com/JerrZzzz/Paper-1.git"
date: "today"
date-format: "long"
abstract: "In this study, we dived into the Apartment Building Evaluation dataset from OpenDataToronto to understand what factors renters prioritize when choosing an apartment. Our focus is on how the year of construction influences rental decisions. By comparing various evaluation scores, such as window quality and building cleanliness, among buildings from different construction years, we discover trends in renter preferences. This research highlight on the significance of a building's age in the rental market, offering valuable insights for both renters and the housing industry."
format: pdf
editor: visual
toc: true
number-sections: true
bibliography: ref.bib
---
